Draft

### 2017-03-01 Draft/sections/misc-math.tex
[minor] Discusses the derivative of dirac function.

\subsection{Gamma Function and Stirling's formula with Stationary phase
approximation/Saddle point approximation}

@@

It has an approximation formula called the Stirling formula. Here I obtain the
Stirling formula with the Saddle point approximation, also called Stationary
phase approximation in pp.108 of \cite{Altland2010}.

Let us further restrict $z$ into $z\in\R$ and $z>0$, the natural logarithm $\ln(z)$ is well
defined, so we have

@@

Let $F(x,z) = -(\ln(x^z)-x)$, then $\frac{dF}{dx}(x_0)=-\frac{z}{x_0}+1=0$ gives the
saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z>0$
confirms that this is really a minimum point. Therefore, the integration is
largely determined by the value around point $x_0=z$. Expanding $F$ around
$x_0=z$, we have
\begin{equation}
    F(x_0 + y)\approx F(x_0=z) + \frac{1}{2z} y^2 
    = z-\ln(z^z) + \frac{1}{2z}y^2
\end{equation}
Therefore
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x} &= 
    \int_0^\infty \dd{x} e^{-F(x,z)} \approx
    \int_{-z}^\infty \dd{y} e^{-z+\ln(z^z) - \frac{1}{2z}y^2}
\end{align}

Now as $z\to\infty$, we have
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{align}
Thus we have
\begin{equation}
    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{equation}
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}

>>>>

\subsection{Gamma Function and Stirling's formula with Stationary phase
approximation}

@@

It has an approximation formula called the Stirling formula. Here I obtain the
Stirling formula with the Stationary phase approximation in pp.108 of
\cite{Altland2010}.

Without further restricting $z$ into $\R$, we can use Stationary phase approximation
to get the result.\footnote{
    If we have restricted $z\in\R$, then instead of Stationary phase
approximation, we would be using Saddle point approximation.}
Note that since $\Re(z)>0$, the natural logarithm $\ln(z)$ is well
defined, so we have

@@

Let $F(x,z) = -(\ln(x^z)-x)$, then $\frac{dF}{dx}(x_0)=-\frac{z}{x_0}+1=0$ gives the
saddle point $x_0=z$. And $\frac{\dd[2]{F}}{\dd x^2}(x_0)=z/x_0^2=1/z$
confirms that this is really a minimum point. Therefore, the integration is
largely determined by the value around point $x_0=z$. Expanding $F$ around
$x_0=z$, we have
\begin{equation}
    F(x_0 + y)\approx F(x_0=z) + \frac{1}{2z} y^2 
    = z-\ln(z^z) + \frac{1}{2z}y^2
\end{equation}
Therefore
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x} &= 
    \int_0^\infty \dd{x} e^{-F(x,z)} \approx
    \int_{-z}^\infty \dd{y} e^{-z+\ln(z^z) - \frac{1}{2z}y^2}
\end{align}

Now as $z\to\infty$, we have
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{align}
Thus we have
\begin{equation}
    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{equation}
For $z\in\C$, $\Re(z)>0$.
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

\subsection{Dirac delta function}

It is quite troublesome to deal with this function $\delta(x)$. For example, sometimes I
have to deal with $\frac{\dd}{\dd{x}}\delta(x)$, or $\delta'(x)$. Here I present an argument, not
proof, of the result.

I treat $\delta(x)$ not as a function, but as an operator. Therefore, we have to
use a test function $f(x)$ to see what $\delta'(x)$ really is. Assuming that the
dirac delta function still follows the rule of \textit{integration by parts}.
Assuming our test function vanishes, or at least does not go to infinity when
$x\to\infty$ or $x\to-\infty$. Then
\begin{align}
    \int_{-\infty}^\infty \dd{x} \delta'(x) f(x) &=
    \eval{\delta(x)f(x)}_{-\infty}^\infty - \int\dd{x}\delta(x)\frac{\dd}{\dd x}f(x)
    = 0 - \dv{f}{x}(0)
\end{align}
Therefore, we say that in this situation,
\begin{equation}
    \delta'(x) = -\delta(x)\dv{x}
\end{equation}

But there is one pitfall that confuses me for a long time. Because:
\begin{align*}
    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
    = -\int\dd{x}g(x)\delta(x)
\end{align*}
This lures me into believing
\begin{equation}
    x\delta'(x) = -\delta(x)
    \label{eq:xdp--d}
\end{equation}
Hence
\begin{equation}
    \delta'(x) = -\frac{\delta(x)}{x}
    \label{eq:dp--dx}
\end{equation}
While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}
